---
title: "Causal inference HW 4"
author: "Adeline Shin"
date: "12/2/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(raster)
library(psych)
library(MatchIt)
library(optmatch)
library(RItools)
library(Matching)
library(rgenoud)
library(texreg)
library(tableone)
library(personalized)
library("MatchIt")
library("lmtest")
library("sandwich")
library("boot")
library("survival")
library("survey")
```

# Upload the Data
```{r}
gardasil_df = read.delim("./gardasil.dat.txt", sep = "") %>% 
    janitor::clean_names()
```

# Question 1
```{r}
# Create subset of data without outcome variable
gardasil_subset = gardasil_df[c(-5)] 

describeBy(gardasil_subset, gardasil_subset$practice_type)
```

# Question 2
The question of interest being addressed in this RCT is whether type of practice where Gardasil vaccine is taken affects rates of completion.

## i) Treatment and Control Arm
In this study, the treatment arm would consist of those who go to an OB-GYN office to receive their gardasil shots, while the control arm would consist of those who go to a general practice or pediatrician to receive their gardasil shots.

## ii) Eligibility Criteria
```{r}
tableone::CreateTableOne(vars = c("age", "age_group", "race", "shots", "insurance_type", "med_assist", "location", "location_type", "practice_type"), strata = "location", data = gardasil_subset)
```

Looking at the descriptive statistics by location, locations 2 and 3 seem to be OB-GYN offices, since they only practice types that correspond to OB-GYN. Furthermore, location 4 does not have any subjects who visit a family practice. Therefore, only location 1 will be included since it is the only one with all three types of practices. This enforces the probabilistic assumption, since it ensures that all subjects have the chance of being a part of either the treatment arm or the control arm.

```{r}
# Check the distribution of age in OB-GYN to see if we need to exclude those under the age of 18
ob_gyn = subset(gardasil_subset, practice_type == 2)
hist(ob_gyn$age)

pediatrician = subset(gardasil_subset, practice_type == 0)
hist(pediatrician$age)

gp = subset(gardasil_subset, practice_type == 1)
hist(gp$age, breaks = 15)
```

Based on the distribution of age in all three locations, we will include all women in the study, since there are both adults and those under the age of 18 in all three practice types.

# Question 3
```{r}
# Only including those who are in location 1
gardasil_included = subset(gardasil_subset, location == 1)

# Creating a group for both general practice and pediatrician offices
gardasil_included = gardasil_included %>% 
    mutate(practice_type = recode(gardasil_included$practice_type, `0` = 0, `1` = 0, `2` = 1))

# New descriptive statistics
describeBy(gardasil_included, gardasil_included$practice_type)
```

Comparing the descriptive statistics created here with those from Question 1, the entirety of group 0 has been left out, since those are the subjects who visited a pediatrics practice for their gardasil vaccine. In addition, there are less subjects in both the OB-GYN and pediatrics groups, since everyone under the age of 18 has been excluded. Therefore, the mean age is a bit higher in both remaining groups. It also looks like the mean number of shots received went down slightly in both groups after excluding those ineligible for the study.

# Question 4
```{r}
# Recode practice_type so that 0 = general practice and 1 = OB-GYN office
ps.model = glm(practice_type ~ age + race + shots + insurance_type + med_assist, data = gardasil_included, family = binomial)

ps = predict(ps.model, type = "response")

summary(ps.model)
```

The following interpretations for the parameter estimates can be made:

* Intercept: The 
* Age: 

# Question 5
```{r}
# Nearest neighbor matching with greedy matching
psmatch1 = matchit(practice_type ~ age + race + shots + insurance_type + med_assist, data = gardasil_included, distance = "logit", method = "nearest", discard = "control")

summary(psmatch1, standardize = TRUE)
plot(psmatch1)
plot(psmatch1, type="hist")
par(mfrow = c(1, 1))
plot(psmatch1, type="jitter", interactive=FALSE)

# Nearest neighbor matching with optimal matching instead of greedy
psmatch2 = matchit(practice_type ~ age + race + shots + insurance_type + med_assist, data = gardasil_included + I(age^2), distance = "logit", method = "optimal")

summary(psmatch2, standardize = TRUE)
plot(psmatch2)
plot(psmatch2, type="hist")
par(mfrow = c(1, 1))
plot(psmatch2, type="jitter", interactive=FALSE)
```

The process for matching involved getting rid of the variables location and location type, since they were the same for all subjects after limiting the eligibility to only those in location 1. Both greedy and optimal methods for matching provide full matching of the treated units, but optimal matching gives better percent balance improvement overall for every variable.

# Question 6
```{r}
# Create matched data for analysis
psmatch2.data = match.data(psmatch2)

# Calculate average treatment effect
psmatch2.mod = svyglm(practice_type ~ age + race + shots + insurance_type + med_assist + I(age^2), data = gardasil_included, design = svydesign(~ 1, weights = ~ weights,data = psmatch2.data))
summary(psmatch2.mod)

psmatch_ate = matchit(practice_type ~ age + race + shots + insurance_type + med_assist + I(age^2), data = gardasil_included, distance = "logit", estimade = "ATT")
psmatchate.data = match.data(psmatch_ate)
psmatchate.mod = svyglm(practice_type ~ age + race + shots + insurance_type + med_assist + I(age^2), design = svydesign(~ 1, weights = ~ weights,data = psmatchate.data))
summary(psmatchate.mod)

# Match the outcome (completed) back to calculate point estimate of ATT
# Create new df of just the subjects included in psmatchate.data

gardasil_ate_df = merge(gardasil_df, psmatchate.data, by = "row.names", all = TRUE)
```

# Question 7
```{r}

```
